---
title: "xcorr Example"
author: "Jason K Freels"
date: "`format(Sys.Date(), '%d %b %Y')`"
output: html_document
---

This is an example of Bayesian estimation using [JAGS](http://mcmc-jags.sourceforge.net/).  This example came from  the [xcorr](https://xcorr.net) blog can be found [HERE](https://xcorr.net/2011/07/13/gibbs-sampling-made-easy-jags-rkward-coda/).  This example assumes that JAGS has been installed and uses the following R packages 

```{r setup, include=FALSE}
library(rjags)
library(coda)
```

## Modeling and Data

The model for this example, written in the JAGS syntax is shown below

```{r}
model <- "xcorrSAT.model"
lines <- readLines(model)
tf <- tempfile()
writeLines(lines, tf)
```

The observed data is 

```{r}
sigma     <- c(15,10,16,11, 9,11,10,18)
schoolobs <- c(28,8, -3, 7,-1, 1,18,12)
```

Using the model and the observed data we can run a Gibbs Sampler with the following code

```{r}
jagresult <- jags.model(tf,
                       data = list('sigma' = sigma,                                                            'schoolobs' = schoolobs,                                                    'N' = 8),
                       n.adapt = 1000)
thesamps <- coda.samples(jagresult,c('mu','tau'),
                         n.iter = 10000,
                         thin = 10,
                         progress.bar = "gui")
```

```{r}
plot(thesamps)
```

