---
title: "Bayes Lectures"
author: "Jason K Freels"
date: "September 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mvtnorm)
```

# Means, variances & covariances of the bivariate normal

```{r}
mu.x <- 921
mu.y <- 5

s.x<-100^2
s.y<-3^2
s.xy<-15^2
```


# Plotting the contours of this bivtnormal

```{r}
x <- seq(610, 1227, by= 1)
y <- seq(0,10,length=length(x))

z<-array(0,dim=c(length(x),length(y)))
Sigma<- matrix(c(s.x,s.xy,s.xy, s.y), 2)

z <- dmvnorm(x=c(x,y),mean=matrix(c(mu.x,mu.y), ncol = 2),sigma=Sigma)

contour(x,y,z,xlab="MPH", ylab="Radial Accuracy",main="F-35 Speed vs Accuracy")
abline(v=mu.x)
abline(h=mu.y)
```

#############################################
#Writing a simple Gibbs sampler
#############################################

mph <- 0    #initial values
rad <- 0    #initial values
B <- 10000
pts <- matrix(NA,ncol=2,nrow=B)

mph<-rnorm(B,mu.x+s.xy*solve(s.y)*(rad-mu.y),sqrt(s.x-s.xy*solve(s.y)*s.xy))
rad<-rnorm(B,mu.y+s.xy*solve(s.x)*(mph-mu.x),sqrt(s.y-s.xy*solve(s.x)*s.xy))
			
pts <- c(mph, rad)


#############################################
#plotting the samples points
#############################################


#############################################
#showing the random walk
#############################################

for(i in 2:1000){

    		points(pts[i-1,1],pts[i-1,2],pch=16)
		time<-Sys.time()
		while(Sys.time()<time+1/sqrt(i)){}

            lines(c(pts[i-1,1], pts[i,1]), c(pts[i-1,2], pts[i-1,2]))
		time<-Sys.time()
		while(Sys.time()<time+1/sqrt(i)){}


		points(pts[i,1],pts[i-1,2],pch=16)
            time<-Sys.time()
		while(Sys.time()<time+1/sqrt(i)){}

		lines(c(pts[i,1], pts[i,1]), c(pts[i-1,2], pts[i,2]))
		time<-Sys.time()
		while(Sys.time()<time+1/sqrt(i)){}


}




#############################################
#showing just the points 
#############################################

contour(x,y,z,xlab="MPH", ylab="Radial Accuracy",main="F-35 Speed vs Accuracy")
abline(v=mu.x)
abline(h=mu.y)


points(pts[,1],pts[,2],pch = 16)
